PANCHANGE_data_preprocessing

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
Corrected some errors. Kept gender only in the NBR COPING data to avoid duplication. Included NBR cohort variable.

nbr.cohort.raw.id <- nbr.cohort.raw %>%
  drop_na(`NBR ID`) %>% # Drop NAs
  distinct(`NBR ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`NBR ID`, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID),
#         startDate.coping = startDate
         ) %>% # Rename startDate
  select(
         Sample, # Sample
         ID, # ID
#         startDate.coping, #Date when participant signed up to NBR COPING
#         Age_uncleaned = age, # Age
         Gender = gender, # Gender
#         Sex = demographics.select_questionnaire_items_medical, #Sex
#         EduYrs = demographics.school_education_school_years.txt, # Years in education
#         demographics.college_or_university_degree, # level of education - univeristy
#         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
#         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
#         demographics.cses_or_equivalent, # level of education - cse
#         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         Ethnicity = ethnicity # Ethnicity
         ) %>%
  add_numeric(., exclude = exclude_cols_dem) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r nbr combine demographics}
if(NBR == TRUE){
dem.raw.id <- merge(nbr.cohort.raw.id, nbr.dem.raw.id, by = "ID")
}
```

```{r nbr demo summary}
if(NBR == TRUE) {
summarytools::dfSummary(
  nbr.cohort.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```

>>>>

nbr.cohort.raw.id <- nbr.cohort.raw %>%
  drop_na(`NBR ID`) %>% # Drop NAs
  distinct(`NBR ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`NBR ID`, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID),
#         startDate.coping = startDate
         ) %>% # Rename startDate
  select(
         Sample, # Sample
         ID, # ID
         Cohort = cohort, #cohort information
#         startDate.coping, #Date when participant signed up to NBR COPING
#         Age_uncleaned = age, # Age
#         Gender = gender, # Gender
#         Sex = demographics.select_questionnaire_items_medical, #Sex
#         EduYrs = demographics.school_education_school_years.txt, # Years in education
#         demographics.college_or_university_degree, # level of education - univeristy
#         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
#         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
#         demographics.cses_or_equivalent, # level of education - cse
#         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         Ethnicity = ethnicity # Ethnicity
         ) %>%
  add_numeric(., exclude = exclude_cols_dem) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r nbr combine demographics}
if(NBR == TRUE){
dem.raw.id <- merge(nbr.cohort.raw.id, nbr.dem.raw.id, by = c("Sample", "ID"))
}
```

```{r nbr demo summary}
if(NBR == TRUE) {
summarytools::dfSummary(
  dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```
